Response to the defense feedback

### 2021-06-04 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Background and Threat Model}
In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.

>>>>

\section{Background and Threat Model}
In this chapter, we treat the side-channel attack as a communication system between two parties.
In the section, we give an overview of the background knowledge of information theory and present the threat model of the chapter.
